### 2017-02-27 MSSM/UncOv.tex
Adding a few more figs to MSSM chapter
More editing

     & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & SR & OS high $m_{T}$ & SS low $m_{T}$ & SS high $m_{T}$ & \\

@@

    \multicolumn{10}{l}{\textbf{Integrated luminosity 13}\TeV} \\

@@

    \multicolumn{10}{l}{\MET \textbf{scale} }\\

@@

    TTT,TTJ,VVT,VVJ & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\

@@

    \multicolumn{4}{l}{\MET \textbf{resolution}} \\

@@

    \multicolumn{10}{l}{\textbf{B-tagging efficiency} }\\

@@

    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\

@@

    \multicolumn{10}{l}{\textbf{High} $P_{T}$ $\tau_h$\textbf{ ID efficiency } } \\

@@

    \multicolumn{10}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting} }\\

@@

    \multicolumn{10}{l}{\textbf{DY reweighting } }\\

@@

    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\

@@

    \multicolumn{10}{l}{\textbf{Normalisation, di-boson} } \\

@@

   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\tau_{h}$ }\\

@@

    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$ } \\

@@

    \multicolumn{10}{l}{\MET \textbf{scale}}\\

@@

    \multicolumn{10}{l}{\MET \textbf{resolution}} \\

@@

    \multicolumn{10}{l}{\textbf{B-mistag rate } }\\

@@

    \multicolumn{10}{l}{\textbf{Jet}$\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\

@@

   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\tau_{h}$ }\\

@@

{\scriptsize

@@

    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\

@@

    \multicolumn{4}{l}{\MET \textbf{scale}} \\

@@

    \multicolumn{4}{l}{Tau-lepton identification and trigger} \\

@@

    \multicolumn{4}{l}{\textbf{B-tagging efficiency} }\\

@@

   \multicolumn{4}{l}{\textbf{B-mistag rate}} \\

@@

    \multicolumn{4}{l}{\textbf{High} $P_{T}$ $\tau_h$ \textbf{ID efficiency}} \\

@@

    \multicolumn{4}{l}{\textbf{DY reweighting } } \\

@@

    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting } } \\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}}\\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\tau_{h}$}\\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\tau_{h}$}\\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\

@@

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the \emu channel.}
{\scriptsize
\begin{tabular}{l|cc|p{5cm}}
   \toprule
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \midrule
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \midrule
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
    \midrule
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \midrule
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \midrule
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \midrule
    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
    All from MC       & 2\%        & 2\% & Fully correlated                              \\
    \midrule
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \midrule
    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
    ZTT,signal      & shape      & shape  & Fully correlated                \\
    \midrule
    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
     ZTT       & shape      & shape & Fully correlated                       \\
   \midrule
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
    TT & shape & shape  & Fully correlated                 \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
    \midrule
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
    QCD & 23\% & 34\% & Fully uncorrelated\\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\bottomrule
\end{tabular}}
\label{tab:SystematicUncertainties_em}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of
or background events in the $Z\rightarrow\mu\mu$ channel.}
{\scriptsize
\begin{tabular}{l|cc|p{5cm}}
   \toprule
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \midrule
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \midrule
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
    \midrule
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \midrule
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \midrule
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \midrule
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
    \bottomrule
\end{tabular}}
\label{tab:SystematicUncertainties_zmm}
\end{center}
\end{table}

>>>>

     & SR & OS high $m_{\text{T}}$ & SS low $m_{\text{T}}$ & SS high $m_{\text{T}}$ & SR & OS high $m_{\text{T}}$ & SS low $m_{\text{T}}$ & SS high $m_{\text{T}}$ & \\

@@

    \multicolumn{10}{l}{\textbf{Integrated luminosity 13 TeV}} \\

@@

    \multicolumn{10}{l}{\MET~\textbf{scale} }\\

@@

    TT(T/J),VV(T/J) & 2\% & & 2\% & &2\% & & 2\% & & uncorr. from ZTT,W \\

@@

    \multicolumn{4}{l}{\MET~\textbf{resolution}} \\

@@

    \multicolumn{10}{l}{\textbf{b-Tagging efficiency} }\\

@@

    \multicolumn{10}{l}{\textbf{light jet mis-tagging rate } }\\

@@

    \multicolumn{10}{l}{\textbf{High}-$p_{\text{T}}$ $\Pgth$\textbf{ ID efficiency } } \\

@@

    \multicolumn{10}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting} }\\

@@

    \multicolumn{10}{l}{\textbf{Drell-Yan reweighting } }\\

@@

    \multicolumn{10}{l}{\textbf{Jet} $\rightarrow\Pgth$ \textbf{fake rate reweighting } }\\

@@

    \multicolumn{10}{l}{\textbf{Normalisation, di-boson + single-top} } \\

@@

   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pgm\Pgm$: $\Pgm$ \textbf{misidentified as} $\Pgth$ }\\

@@

    \multicolumn{10}{l}{\textbf{Normalisation,} $\PZ$\textbf{+jets : jet misidentified as} $\Pgth$ } \\

@@

    \multicolumn{10}{l}{\MET~\textbf{scale}}\\

@@

    \multicolumn{10}{l}{\MET~\textbf{resolution}} \\

@@

    \multicolumn{10}{l}{\textbf{Light jet mis-tagging rate } }\\

@@

    \multicolumn{10}{l}{\textbf{Jet} $\rightarrow\tau_h$ \textbf{fake rate reweighting } }\\

@@

   \multicolumn{10}{l}{ \textbf{Normalisation,} $\PZ\to\Pe\Pe$: $\Pe$ \textbf{misidentified as} $\Pgth$ }\\

@@

@@

    \multicolumn{4}{l}{\textbf{Integrated luminosity 13 TeV}}\\

@@

    \multicolumn{4}{l}{\MET~\textbf{scale}} \\

@@

    \multicolumn{4}{l}{\textbf{Tau-lepton identification and trigger}} \\

@@

    \multicolumn{4}{l}{\textbf{b-Tagging efficiency} }\\

@@

   \multicolumn{4}{l}{\textbf{Light jet mis-tagging rate}} \\

@@

    \multicolumn{4}{l}{\textbf{High}-$p_{\text{T}}$ $\Pgth$ \textbf{ID efficiency}} \\

@@

    \multicolumn{4}{l}{\textbf{Drell-Yan reweighting } } \\

@@

    \multicolumn{4}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting } } \\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, di-boson + single-top}}\\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ\to\Pe\Pe$: $\Pe$\textbf{ misidentified as }$\Pgth$}\\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$\textbf{+jets : jet misidentified as} $\Pgth$}\\

@@

    \multicolumn{4}{l}{\textbf{Normalisation, \Wjets }}\\

@@

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the \emu channel.}
{\scriptsize
\begin{tabular}{l|cc|p{5cm}}
   \toprule
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \midrule
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \midrule
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13 TeV}}\\
    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
    \midrule
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \midrule
    \multicolumn{4}{l}{\MET~\textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \midrule
   \multicolumn{4}{l}{\MET~\textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \midrule
    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
    All from MC       & 2\%        & 2\% & Fully correlated                              \\
    \midrule
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
    \midrule
    \multicolumn{4}{l}{\textbf{b-Tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \midrule
    \multicolumn{4}{l}{\textbf{Light jet mis-tagging rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \midrule
    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
    ZTT,signal      & shape      & shape  & Fully correlated                \\
    \midrule
    \multicolumn{4}{l}{\textbf{Drell-Yan reweighting }}\\
     ZTT       & shape      & shape & Fully correlated                       \\
   \midrule
    \multicolumn{4}{l}{\textbf{Top quark} $p_{\text{T}}$ \textbf{reweighting}}\\
    TT & shape & shape  & Fully correlated                 \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
    \midrule
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson + single-top}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
    QCD & 23\% & 34\% & Fully uncorrelated\\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, \Wjets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\bottomrule
\end{tabular}}
\label{tab:SystematicUncertainties_em}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of
or background events in the $Z\rightarrow\mu\mu$ channel.}
{\scriptsize
\begin{tabular}{l|cc|p{5cm}}
   \toprule
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \midrule
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \midrule
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13 TeV}}\\
    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
    \midrule
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \midrule
    \multicolumn{4}{l}{\MET~\textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \midrule
   \multicolumn{4}{l}{\MET~\textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \midrule
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
    \midrule
    \multicolumn{4}{l}{\textbf{b-Tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \midrule
    \multicolumn{4}{l}{\textbf{Light jet mis-tagging rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson + single-top}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, \Wjets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
    \bottomrule
\end{tabular}}
\label{tab:SystematicUncertainties_zmm}
\end{center}
\end{table}
